\thetitle

### 2022-04-04 paper/paper.tex
table summarizing algorithms

% Language selector
\newif\ifen
\entrue % Change to false to export Korean

@@

\renewcommand{\abstractname}{요약}
\begin{abstract}
본 논문은 다수의 확률 변수로 구성된 포트폴리오의 기대 최대값을 예산 조건 하에서 최대화하는 문제를 고려한다. 이를 대학 지원 최적화 문제라고 부른다. 각 확률 변수의 비용, 즉 각 대학의 지원 비용이 동일한 경우, 최적 포트폴리오는 예산 제약식으로 결정된 포함 사슬 관계 성질을 가짐을 보이고 이를 바탕으로 다항 시간 해법을 제시한다. 대학의 지원 비용이 서로 다른 경우, 문제가 NP-complete함을 증명한다. 3가지 일반적인 해법을 도출한다. 첫째는 분지한계 기반 해법이다. 둘째는 의사 다항 시간 안에 정확한 해를 출력하는 동적 계획 해법이다. 마지막으로 다른 동적 계획 기반으로 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme)이 존재함을 보인다. 수리적 실험을 통해서 알고리즘의 현실성을 보인다.

@@

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.  Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to formulate the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 급료는 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용해서 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정된다는 넓은 인식에 따라, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략을 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

@@

\ifen
In Section \ref{homogappcosts}, we consider the special case where each $g_j = 1$ and $H$ is an integer $h \leq m$.  We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm. Then, we show that the optimal portfolios are nested in the budget constraint, which yields an exact algorithm that runs in $O(hm)$-time.
\else
\ref{homogappcosts}절에서 각 $g_j = 1$이고 $H$가 $h \leq m$이고 자연수인 특수한 경우를 고려한다. 직관적인 휴리스틱 해법이 실제로 $1/h$-근사 해법임을 증명한다. 그다음에 최적 포트폴리오의 예산 제약에 대한 포함 사슬 관계를 보이고 이를 이용해서 $O(hm)$-시간 정확한 해법을 도출한다.
\fi

\ifen
In Section \ref{hetappcosts}, we turn to the scenario in which colleges differ in their application fees. We show that the decision form of the portfolio optimization problem is NP-complete through a polynomial reduction from the binary knapsack problem. We provide three algorithms for this more general setup. The first is a branch-and-bound routine. The second is a dynamic program that iterates on total expenditures and produces an exact solution in pseudopolynomial time, namely $O(Hm + m \log m)$. The third is a different dynamic program that iterates on truncated portfolio valuations. It yields a fully polynomial-time approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in $O(m^3 / \varepsilon)$ time.  
\else
\ref{hetappcosts}절에서 각 학교의 지원 비용이 동일하지 않은 일반적인 상황을 다룬다. 이진 배낭 문제에서의 다항 변환을 통해서 포트폴리오 최적화 문제가 NP-complete함을 증명한다. 또한 3개의 일반적인 해법을 제안한다. 첫째는 분지한계법이다. 둘째는 총 지출액으로 탐색하는 $O(Hm + m \log m)$과 같은 의사 다항 시간 동적 계획 해법이다. 셋째는 실수값을 분수값으로 내림한 포트폴리오 가치를 탐색하는 또다른 동적 계획 해법이다. 이를 통해서 $O(m^3 / \varepsilon)$-시간 안에 $(1 - \varepsilon)$-근사해를 출력하는 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme)을 얻는다.
\fi

@@

\ifen \section{Homogeneous application costs}  \else \section{동일한 지원 비용} \fi \label{homogappcosts}
\ifen In this section, we focus on the special case in which each $g_j = 1$ and $H$ is a natural number $h \leq m$.   We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm, then derive an exact polynomial-time solution algorithm.
This case is similar to the centralized college admissions process in Korea, where there is no application fee, but by law, students are allowed to apply to no more than $h$ schools. (In the Korean case, $m=202$ and $h=3$.) Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$ unless otherwise noted. Throughout this section, we will call the applicant Alma, and refer to the corresponding optimization problem as Alma's problem. 
\else
본 절에서 모든 $g_j = 1$이며 $H$가 자연수 $h \leq m$인 특수한 경우에 집중한다. 직관적인 휴리스틱 해법이 실제로 $1/h$-근사 해법임을 보인 다음에 정확한 다항 시간 해법을 도출한다. 이 특수한 경우는 지원 비용이 없으며 국가 법에 따라 최대 $h$개의 학교에 지원할 수 있는 한국의 중심화된 대학 지원 과정과 비슷하다. (한국 경우,  $m=202$이고 $h=3$이다.) 정리 \ref{assumetzerozero}을(를) 적용해서 다른 언급이 없으면 $t_0 = 0$임을 가정하자. 본 절 내내 지원자를 `알마'라고 부르고 해당 최적화 문제를 `알마의 문제'라고 부른다.
\fi

@@

\ifen \subsection{Approximation properties of a na\"ive solution}  \else \subsection{나이브 해법의 근사 성질} \fi
\ifen
The expected utility associated with a single school $c_j$ is simply $\operatorname{E}[t_j Z_j] = f_j t_j$. It is therefore tempting to adopt the following strategy, which turns out to be inoptimal.
\else 
단일 학교 $c_j$에 해당하는 기대 효용이 단순히 $\operatorname{E}[t_j Z_j] = f_j t_j$이므로 다음과 같은 알고리즘이 매력적으로 보일 수 있지만 사실은 최적해가 아니다.
\fi
\begin{definition}[\ifen Na\"ive algorithm for Alma’s problem\else 알마의 문제를 위한 나이브 해법\fi] \label{naivealgorithm}
\ifen 
Apply to the $h$ schools having the highest expected utility $f_j t_j$.
\else
기대 효용 $f_j t_j$가 가장 높은 $h$개의 학교로 지원한다.
\fi
\end{definition}
\ifen 
The basic error of this algorithm is that it maximizes $\operatorname{E}\left[\sum t_j Z_j \right]$ instead of $\operatorname{E}\left[\max \{t_j Z_j\} \right]$. The latter is what Alma is truly concerned with, since in the end she can attend only one school. The following example shows that the na\"ive algorithm can produce a suboptimal solution.
\else
위 알고리즘의 기본 실수는 $\operatorname{E}\left[\max \{t_j Z_j\} \right]$ 대신  $\operatorname{E}\left[\sum t_j Z_j \right]$을 최대화하는 것이다. 결국에는 단 한 학교로만 진학할 수 있으므로 알마의 목적은 후자가 아닌 전자다. %학교 개별 효용의 기대 최대값이다. 
다음 예는 나이브 해법이 최적해가 아닌 해를 출력할 수 있음을 보인다.
\fi
\begin{example}
\ifen 
Suppose $m=3$, $h=2$,  $ t= (70, 80, 90) $, and $f = (0.4, 0.4, 0.3)$. 
%\implies t * f &= (28, 32, 27)
%\begin{align*}
%t &= (70, 80, 90) \\
%f &= (0.4, 0.4, 0.3) \\
%\implies t * f &= (28, 32, 27)
%\end{align*}
Then the na\"ive algorithm picks $\mathcal{T} = \{1, 2\}$ with 
$v(\mathcal{T}) = 70(0.4)(1-0.4) + 80(0.4) = 48.8$.
But $\mathcal{X} = \{2, 3\}$ with
$v(\mathcal{X}) = 80(0.4)(1-0.3) + 90(0.3) = 49.4$
is the optimal solution. 
\else
$m=3$, $h=2$,  $ t= (70, 80, 90) $, 그리고 $f = (0.4, 0.4, 0.3)$이라고 하자. 그러면 나이브 해법은 $\mathcal{T} = \{1, 2\}$를 선택하며 그의 기대 효용은 $v(\mathcal{T}) = 70(0.4)(1-0.4) + 80(0.4) = 48.8$이다. 그러나 $\mathcal{X} = \{2, 3\}$를 선택하면 기대 효용은 $v(\mathcal{X}) = 80(0.4)(1-0.3) + 90(0.3) = 49.4$이고 이는 최적해다.
\fi
\end{example}

@@

\ifen (Inductive step.) Assume that $\mathcal{X}_1 \subset \cdots \subset \mathcal{X}_h$, and we will show $\mathcal{X}_h \subset \mathcal{X}_{h+1}$. Let $k = \argmax\{ t_k: k \in \mathcal{X}_{h+1}\}$ and write $\mathcal{X}_{h+1} = \mathcal{Y}_{h} \cup \{k\}$.
\else (추론.) $\mathcal{X}_1 \subset \cdots \subset \mathcal{X}_h$라고 가정하고 $\mathcal{X}_h \subset \mathcal{X}_{h+1}$임을 보이자. $k = \argmax\{ t_k: k \in \mathcal{X}_{h+1}\}$으로 정의해서 $\mathcal{X}_{h+1} = \mathcal{Y}_{h} \cup \{k\}$으로 표현하자.\fi

@@

\ifen We will use the function $w(\mathcal{Y})$ to grade portfolios $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$ according to how well they complement $\{k\}$. To construct $w(\mathcal{Y})$, let $\tilde t_j$ denote the expected utility Alma receives from school $c_j$ \emph{given} that she has been admitted to $c_j$ and applied to $c_k$. For $j < k$, including $j = 0$, this is $\tilde t_j = (1- f_k) t_j + f_k t_k$; for $j > k $, this is $\tilde t_j = t_j$. This means that 
\else 함수 $w(\mathcal{Y})$를 이용해서 $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$인 포트폴리오와 $\{k\}$ 사이의 \mbox{`보완성'을} 평가하자. $w(\mathcal{Y})$를 구성하기 위해, 알마가 $c_j$에 합격한 상황에서 $c_k$에 지원했을 때 $c_j$에서 받는 조건부 기대 효용을 $\tilde t_j$라고 하자. $j = 0$을 포함한 $j < k$에 대해 이값은 $\tilde t_j = t_j (1- f_k) + t_k f_k$이며, $j > k $에 대해 $\tilde t_j = t_j$임을 알 수 있다. 따라서 \fi
\begin{equation}\label{Vyastildet}
v(\mathcal{Y}\cup\{k\}) = \sum_{j \in \{0\} \cup \mathcal{Y}} \tilde t_j p_j(\mathcal{Y}).\end{equation}
\ifen The transformation to $\tilde t$ does not change the order of the $t_j$-values. Therefore, the expression on the right side of \eqref{Vyastildet} is itself a portfolio valuation function. In the corresponding market, $t$ is replaced by $\tilde t$ and $\mathcal{C}$ is replaced by $\mathcal{C}\setminus\{k\}$. Now, we obtain $w(\mathcal{Y})$ through one more transformation: Define $\bar t_j = \tilde t_j - \tilde t_0$ so that $t_0 = 0$ and let
\else $\tilde t$로 변환하면 $t_j$의 순서가 변하지 않기 때문에 \eqref{Vyastildet}의 우변 그 자체가 포트폴리오 가치 함수이다. $t$를 $\tilde t$로, $\mathcal{C}$를 $\mathcal{C}\setminus \{k\}$로 대체하면 대응하는 시장이 된다. 이제 또 하나의 변환을 적용한다. $t_0 = 0$이 되도록 $\bar t_j = \tilde t_j - \tilde t_0$으로 정의하고 $w(\mathcal{Y})$를 다음과 같이 얻을 수 있다. \fi
\begin{equation}  \label{wYvXminusconst}
w(\mathcal{Y})
= \sum_{j \in \{0\} \cup \mathcal{Y}} \bar t_j p_j(\mathcal{Y})
= \sum_{j \in \{0\} \cup \mathcal{Y}} \tilde t_j p_j(\mathcal{Y})- \tilde t_0
= v(\mathcal{Y}\cup\{k\}) -  f_k t_k \end{equation}
\ifen where the second equality follows from Theorem \ref{assumetzerozero}. This identity says that the optimal complements to $\{k\}$, given by $\mathcal{Y}_{h-1}$ and $\mathcal{Y}_h$, are themselves optimal portfolios of size $h-1$ and $h$ for the market whose objective function is $w(\mathcal{Y})$. Since $\bar t_0 = 0$ in the latter market, the inductive hypothesis implies that $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$, which completes the proof.\footnote{We thank Yim Seho for discovering this useful transformation.}
\else 두번째 등호는 정리 \ref{assumetzerozero}에 따라 성립한다. 이 등호는, $\{k\}$와 최적으로 보완적인 $\mathcal{Y}_{h-1}$과 $\mathcal{Y}_h$는 목적함수가 $w(\mathcal{Y})$인 시장에서 각각 크기가 $h-1$과 $h$인 최적 포트폴리오임을 의미한다. 새로운 시장에서 $\bar t_0 = 0$이므로 귀납법 가설을 적용하면 $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$임을 알 수 있다. 따라서 증명이 완성된다.\footnote{이 유용한 변환을 발견한 임세호에게 감사를 표한다.} \fi
\end{proof}

@@

\ifen 
We reduce the computation time to $O(hm)$ by taking advantage of the transformation from the inductive step in the proof of Theorem \ref{nestedapplication}. Once school $k$ is added to $\mathcal{X}$, we remove it from the set $\mathcal{C}\setminus \mathcal{X}$ of candidates, and update the $t_j$-values of the remaining schools according to the following transformation:
\else
정리 \ref{nestedapplication} 증명의 추론 단계에서 제시한 변환을 활용하면 계산 시간을 $O(hm)$으로 감소시킬 수 있다. $\mathcal{X}$에 $k$를 추가하면, 후보자 집합인 $\mathcal{C}\setminus \mathcal{X}$에서 $k$를 제거하고 남은 학교의 $t_j$-값은 다음처럼 수정한다.
\fi
\begin{align}\label{howtotransformfj}
\bar t_j = 
\begin{cases}
(1 - f_k) t_j, \quad & t_j \leq t_k \\
t_j - f_k t_k, \quad& t_j > t_k
\end{cases}
\end{align}
\ifen
It is easy to verify that this is the composition of the two transformations (from $t$ to $\tilde t$, and from $\tilde t$ to $\bar t$) given in the proof. Now, the \emph{next} school added must be the optimal singleton portfolio in the modified market. But the optimal singleton portfolio consists simply of the school with the highest value of $f_j \bar t_j$. Therefore, by updating the $t_j$-values at each iteration according to \eqref{howtotransformfj}, we eliminate the need to compute $v(\mathcal{X})$ entirely. Moreover, this algorithm does not require the schools to be indexed in ascending order by $t_j$, which removes the $O(m\log m)$ sorting cost.
\else
이것이 증명에서 정의한 두개의 변환($t$에서 $\tilde t$로, 그리고 $\tilde t$에서 $\bar t$로)의 합성임을 쉽게 확인할 수 있다. 그러면 다음으로 추가하는 학교는 수정된 시장의 최적 단일 원소 포트폴리오가 되어야 한다. 그런데 최적 단일 원소 포트폴리오는 단순히 $f_j \bar t_j$가 가장 높은 학교로 이루어진다. 따라서 각 반복단계에서 \eqref{howtotransformfj}을(를) 이용해서 $t_j$-값을 수정하면 $v(\mathcal{X})$를 계산할 필요가 완전히 없어진다. 게다가 이 알고리즘에서 $t_j$를 배열할 필요가 없으므로 $O(m\log m)$인 배열 비용이 사라진다.
\fi

>>>>

\usepackage{stackengine}
\newcommand\xrowht[2][0]{\addstackgap[.5\dimexpr#2\relax]{\vphantom{#1}}}

% Language selector
\newif\ifen
\enfalse % Change to false to export Korean

@@

\renewcommand{\abstractname}{요약}
\begin{abstract}
본 논문은 다수의 확률 변수로 구성된 포트폴리오의 기대 최대값을 예산 조건 하에서 최대화하는 문제를 고려한다. 이를 대학 지원 최적화 문제라고 부른다. 각 확률 변수의 비용, 즉 각 대학의 지원 비용이 동일한 경우, 최적 포트폴리오는 예산 제약식으로 결정된 포함 사슬 관계 성질을 가짐을 보이고 이를 바탕으로 다항 시간 해법을 제시한다. 대학의 지원 비용이 서로 다른 경우, 문제가 NP-complete함을 증명한다. 3가지 일반적인 해법을 도출한다. 첫째는 분지한계 기반 해법이다. 둘째는 의사 다항 시간 안에 정확한 해를 출력하는 동적 계획 해법이다. 마지막으로 다른 동적 계획 기반으로 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme)이 존재함을 보인다. 수리적 실험을 통하여 알고리즘의 현실성을 보인다.

@@

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.  Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to formulate the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 급료는 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용하여 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정된다는 넓은 인식에 따라, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략을 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

@@

\ifen
In Section \ref{homogappcosts}, we consider the special case where each $g_j = 1$ and $H$ is an integer $h \leq m$.  We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm. Then, we show that the optimal portfolios are nested in the budget constraint, which yields an exact algorithm that runs in $O(hm)$-time.
\else
\ref{homogappcosts}절에서 각 $g_j = 1$이고 $H$가 $h \leq m$이고 자연수인 특수한 경우를 고려한다. 직관적인 휴리스틱 해법이 실제로 $1/h$-근사 해법임을 증명한다. 그다음에 최적 포트폴리오의 예산 제약에 대한 포함 사슬 관계를 보이고 이를 이용하여 $O(hm)$-시간 정확한 해법을 도출한다.
\fi

\ifen
In Section \ref{hetappcosts}, we turn to the scenario in which colleges differ in their application fees. We show that the decision form of the portfolio optimization problem is NP-complete through a polynomial reduction from the binary knapsack problem. We provide three algorithms for this more general setup. The first is a branch-and-bound routine. The second is a dynamic program that iterates on total expenditures and produces an exact solution in pseudopolynomial time, namely $O(Hm + m \log m)$. The third is a different dynamic program that iterates on truncated portfolio valuations. It yields a fully polynomial-time approximation scheme that produces a $(1 - \varepsilon)$-optimal solution in $O(m^3 / \varepsilon)$ time.  
\else
\ref{hetappcosts}절에서 각 학교의 지원 비용이 동일하지 않은 일반적인 상황을 다룬다. 이진 배낭 문제에서의 다항 변환을 통하여 포트폴리오 최적화 문제가 NP-complete함을 증명한다. 또한 3개의 일반적인 해법을 제안한다. 첫째는 분지한계법이다. 둘째는 총 지출액으로 탐색하는 $O(Hm + m \log m)$과 같은 의사 다항 시간 동적 계획 해법이다. 셋째는 실수값을 분수값으로 내림한 포트폴리오 가치를 탐색하는 또다른 동적 계획 해법이다. 이를 통하여 $O(m^3 / \varepsilon)$-시간 안에 $(1 - \varepsilon)$-근사해를 출력하는 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme)을 얻는다.
\fi

@@

\ifen \section{Homogeneous application costs}  \else \section{동일한 지원 비용} \fi \label{homogappcosts}
\ifen In this section, we focus on the special case in which each $g_j = 1$ and $H$ is a natural number $h \leq m$.   We show that an intuitive heuristic is in fact a $1/h$-approximation algorithm, then derive an exact polynomial-time solution algorithm.
This case is similar to the centralized college admissions process in Korea, where there is no application fee, but by law, students are allowed to apply to no more than $h$ schools. (In the Korean case, $m=202$ and $h=3$.) Applying Theorem \ref{assumetzerozero}, we assume that $t_0 = 0$ unless otherwise noted. Throughout this section, we will call the applicant Alma, and refer to the corresponding optimization problem as Alma's problem. 
\else
본 절에서 모든 $g_j = 1$이며 $H$가 자연수 $h \leq m$인 특수한 경우에 집중한다. 직관적인 휴리스틱 해법이 실제로 $1/h$-근사 해법임을 보인 다음에 정확한 다항 시간 해법을 도출한다. 이 특수한 경우는 지원 비용이 없으며 국가 법에 따라 최대 $h$개의 학교에 지원할 수 있는 한국의 중심화된 대학 지원 과정과 비슷하다. (한국 경우,  $m=202$이고 $h=3$이다.) 정리 \ref{assumetzerozero}을(를) 적용하여 다른 언급이 없으면 $t_0 = 0$임을 가정하자. 본 절 내내 지원자를 `알마'라고 부르고 해당 최적화 문제를 `알마의 문제'라고 부른다.
\fi

@@

\ifen \subsection{Approximation properties of a na\"ive solution}  \else \subsection{나이브 해법의 근사 성질} \fi
\ifen
The expected utility associated with a single school $c_j$ is simply $\operatorname{E}[t_j Z_j] = f_j t_j$. It is therefore tempting to adopt the following strategy, which turns out to be inoptimal.
\else 
단일 학교 $c_j$에 해당하는 기대 효용이 단순히 $\operatorname{E}[t_j Z_j] = f_j t_j$이므로 다음과 같은 알고리즘이 매력적으로 보일 수 있지만 사실은 최적해가 아니다.
\fi
\begin{definition}[\ifen Na\"ive algorithm for Alma’s problem\else 알마의 문제를 위한 나이브 해법\fi] \label{naivealgorithm}
\ifen 
Apply to the $h$ schools having the highest expected utility $f_j t_j$.
\else
기대 효용 $f_j t_j$가 가장 높은 $h$개의 학교로 지원한다.
\fi
\end{definition}
\ifen 
\noindent This algorithm's computation time is $O(m)$ using the \small PICK \normalsize algorithm of Blum et al. (1973).

The basic error of the na\"ive algorithm is that it maximizes $\operatorname{E}\left[\sum t_j Z_j \right]$ instead of $\operatorname{E}\left[\max \{t_j Z_j\} \right]$. The latter is what Alma is truly concerned with, since in the end she can attend only one school. The following example shows that the na\"ive algorithm can produce a suboptimal solution.
\else
\noindent Blum 외 (1973)의 \small PICK \normalsize 알고리즘을 사용하면 위의 해법의 계산 시간이 $O(m)$이다.

나이브 알고리즘의 기본 실수는 $\operatorname{E}\left[\max \{t_j Z_j\} \right]$ 대신  $\operatorname{E}\left[\sum t_j Z_j \right]$을 최대화하는 것이다. 결국에는 단 한 학교로만 진학할 수 있으므로 알마의 목적은 후자가 아닌 전자다. %학교 개별 효용의 기대 최대값이다. 
다음 예는 나이브 해법이 최적해가 아닌 해를 출력할 수 있음을 보인다.
\fi
\begin{example}
\ifen 
Suppose $m=3$, $h=2$,  $ t= (70, 80, 90) $, and $f = (0.4, 0.4, 0.3)$. 
%\implies t * f &= (28, 32, 27)
%\begin{align*}
%t &= (70, 80, 90) \\
%f &= (0.4, 0.4, 0.3) \\
%\implies t * f &= (28, 32, 27)
%\end{align*}
Then the na\"ive algorithm picks $\mathcal{T} = \{1, 2\}$ with 
$v(\mathcal{T}) = 70(0.4)(1-0.4) + 80(0.4) = 48.8$.
But $\mathcal{X} = \{2, 3\}$ with
$v(\mathcal{X}) = 80(0.4)(1-0.3) + 90(0.3) = 49.4$
is the optimal solution. 
\else
$m=3$, $h=2$,  $ t= (70, 80, 90) $, 그리고 $f = (0.4, 0.4, 0.3)$이라고 하자. 그러면 나이브 해법은 $\mathcal{T} = \{1, 2\}$를 선택하며 그의 기대 효용은 $v(\mathcal{T}) = 70(0.4)(1-0.4) + 80(0.4) = 48.8$이다. 그러나 $\mathcal{X} = \{2, 3\}$를 선택하면 기대 효용은 $v(\mathcal{X}) = 80(0.4)(1-0.3) + 90(0.3) = 49.4$이고 이는 최적해다.
\fi
\end{example}

@@

\ifen (Inductive step.) Assume that $\mathcal{X}_1 \subset \cdots \subset \mathcal{X}_h$, and we will show $\mathcal{X}_h \subset \mathcal{X}_{h+1}$. Let $k = \argmax\{ t_k: k \in \mathcal{X}_{h+1}\}$ and write $\mathcal{X}_{h+1} = \mathcal{Y}_{h} \cup \{k\}$.
\else (추론.) $\mathcal{X}_1 \subset \cdots \subset \mathcal{X}_h$라고 가정하고 $\mathcal{X}_h \subset \mathcal{X}_{h+1}$임을 보이자. $k = \argmax\{ t_k: k \in \mathcal{X}_{h+1}\}$으로 정의하여 $\mathcal{X}_{h+1} = \mathcal{Y}_{h} \cup \{k\}$으로 표현하자.\fi

@@

\ifen We will use the function $w(\mathcal{Y})$ to grade portfolios $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$ according to how well they complement $\{k\}$. To construct $w(\mathcal{Y})$, let $\tilde t_j$ denote the expected utility Alma receives from school $c_j$ \emph{given} that she has been admitted to $c_j$ and applied to $c_k$. For $j < k$, including $j = 0$, this is $\tilde t_j = (1- f_k) t_j + f_k t_k$; for $j > k $, this is $\tilde t_j = t_j$. This means that 
\else 함수 $w(\mathcal{Y})$를 이용하여 $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$인 포트폴리오와 $\{k\}$ 사이의 \mbox{`보완성'을} 평가하자. $w(\mathcal{Y})$를 구성하기 위해, 알마가 $c_j$에 합격한 상황에서 $c_k$에 지원했을 때 $c_j$에서 받는 조건부 기대 효용을 $\tilde t_j$라고 하자. $j = 0$을 포함한 $j < k$에 대해 이값은 $\tilde t_j = t_j (1- f_k) + t_k f_k$이며, $j > k $에 대해 $\tilde t_j = t_j$임을 알 수 있다. 따라서 \fi
\begin{equation}\label{Vyastildet}
v(\mathcal{Y}\cup\{k\}) = \sum_{j \in \{0\} \cup \mathcal{Y}} \tilde t_j p_j(\mathcal{Y}).\end{equation}
\ifen The transformation to $\tilde t$ does not change the order of the $t_j$-values. Therefore, the expression on the right side of \eqref{Vyastildet} is itself a portfolio valuation function. In the corresponding market, $t$ is replaced by $\tilde t$ and $\mathcal{C}$ is replaced by $\mathcal{C}\setminus\{k\}$. Now, we obtain $w(\mathcal{Y})$ through one more transformation: Define $\bar t_j = \tilde t_j - \tilde t_0$ so that $t_0 = 0$ and let
\else $\tilde t$로 변환하면 $t_j$의 순서가 변하지 않기 때문에 \eqref{Vyastildet}의 우변 그 자체가 포트폴리오 가치 함수이다. $t$를 $\tilde t$로, $\mathcal{C}$를 $\mathcal{C}\setminus \{k\}$로 대체하면 대응하는 시장이 된다. 이제 또 하나의 변환을 적용한다. $t_0 = 0$이 되도록 $\bar t_j = \tilde t_j - \tilde t_0$으로 정의하고 $w(\mathcal{Y})$를 다음과 같이 얻을 수 있다. \fi
\begin{equation}  \label{wYvXminusconst}
w(\mathcal{Y})
= \sum_{j \in \{0\} \cup \mathcal{Y}} \bar t_j p_j(\mathcal{Y})
= \sum_{j \in \{0\} \cup \mathcal{Y}} \tilde t_j p_j(\mathcal{Y})- \tilde t_0
= v(\mathcal{Y}\cup\{k\}) -  f_k t_k \end{equation}
\ifen where the second equality follows from Theorem \ref{assumetzerozero}. This identity says that the optimal complements to $\{k\}$, given by $\mathcal{Y}_{h-1}$ and $\mathcal{Y}_h$, are themselves optimal portfolios of size $h-1$ and $h$ for the market whose objective function is $w(\mathcal{Y})$. Since $\bar t_0 = 0$ in the latter market, the inductive hypothesis implies that $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$, which completes the proof.\footnote{We thank Yim Seho for discovering this useful transformation.}
\else 두번째 등호는 정리 \ref{assumetzerozero}에 따라 성립한다. 이 등호는, $\{k\}$와 최적으로 보완적인 $\mathcal{Y}_{h-1}$과 $\mathcal{Y}_h$는 목적함수가 $w(\mathcal{Y})$인 시장에서 각각 크기가 $h-1$과 $h$인 최적 포트폴리오임을 의미한다. 새로운 시장에서 $\bar t_0 = 0$이므로 귀납법 가설을 적용하면 $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$임을 알 수 있다. 따라서 증명이 완성된다.\footnote{이 유용한 변환을 발견한 임세호에게 감사를 표한다.} \fi
\end{proof}

@@

\ifen 
We reduce the computation time to $O(hm)$ by taking advantage of the transformation from the inductive step in the proof of Theorem \ref{nestedapplication}. Once school $k$ is added to $\mathcal{X}$, we eliminate it from the set $\mathcal{C}\setminus \mathcal{X}$ of candidates, and update the $t_j$-values of the remaining schools according to the following relation.
\else
정리 \ref{nestedapplication} 증명의 추론 단계에서 제시한 변환을 활용하면 계산 시간을 $O(hm)$으로 감소시킬 수 있다. $\mathcal{X}$에 $k$를 추가하면, 후보자 집합인 $\mathcal{C}\setminus \mathcal{X}$에서 $k$를 소거하고 남은 학교의 $t_j$-값을 다음처럼 수정한다.
\fi
\begin{proposition}[\ifen Eliminate $c_k$\else $c_k$ 소거\fi]
\ifen For $\mathcal{X} \subseteq \mathcal{C} \setminus \{k\}$, $v(\mathcal{X}\cup\{k\}; t)  = v(\mathcal{X}; \bar t) + f_k t_k$, where
\else $\mathcal{X} \subseteq \mathcal{C} \setminus \{k\}$에 대해, $v(\mathcal{X}\cup\{k\}; t)  = v(\mathcal{X}; \bar t) + f_k t_k$이다. 단,\fi
\begin{align}\label{howtotransformfj}
\bar t_j = 
\begin{cases}
(1 - f_k) t_j, \quad & t_j \leq t_k \\
t_j - f_k t_k, \quad& t_j > t_k.
\end{cases}
\end{align}
\end{proposition}%
\ifen
\noindent It is easy to verify that \eqref{howtotransformfj} is the composition of the two transformations (from $t$ to $\tilde t$, and from $\tilde t$ to $\bar t$) given in the proof. (We will reuse this transformation as a variable-elimination technique in the branch-and-bound algorithm presented in Subsection \ref{subsectionbranchbound}.)

Now, the \emph{next} school added must be the optimal singleton portfolio in the modified market. But the optimal singleton portfolio consists simply of the school with the highest value of $f_j \bar t_j$. Therefore, by updating the $t_j$-values at each iteration according to \eqref{howtotransformfj}, we eliminate the need to compute $v(\mathcal{X})$ entirely. Moreover, this algorithm does not require the schools to be indexed in ascending order by $t_j$, which removes the $O(m\log m)$ sorting cost.
\else
\noindent \eqref{howtotransformfj}이(가) 증명에서 정의한 두개의 변환($t$에서 $\tilde t$로, 그리고 $\tilde t$에서 $\bar t$로)의 합성임을 쉽게 확인할 수 있다. (항 \ref{subsectionbranchbound}에서 제시하는 분지한계법에서 이 변환을 변수 소거법으로 재활용한다.)

그러면 다음으로 추가하는 학교는 수정된 시장의 최적 단일 원소 포트폴리오가 되어야 한다. 그런데 최적 단일 원소 포트폴리오는 단순히 $f_j \bar t_j$가 가장 높은 학교로 이루어진다. 따라서 각 반복단계에서 \eqref{howtotransformfj}을(를) 이용하여 $t_j$-값을 수정하면 $v(\mathcal{X})$를 계산할 필요가 완전히 없어진다. 게다가 이 알고리즘에서 $t_j$를 배열할 필요가 없으므로 $O(m\log m)$인 배열 비용이 사라진다. 
\fi
